---
title: "What Wins in the NFL?"
Author: Michael Rodriguez
date: "6/5/2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

## loading the neccessary packages and spreadsheet

```{r}
library(ggplot2)
library(stats)
library(corrplot)
library(readxl)
NFL <- read_excel("C:/Users/Owner/Desktop/Excel Workbooks/NFL.xlsx")
```

## now we run a pearson corr test to find any significant relationships
```{r}
cor(NFL,method = "pearson")

```


## for a more visual look at the corrlations, assign the corr to a variable
```{r}
NFLCorr<-cor(NFL,method = "pearson")
```

## now we can use this new variable to make a few visualizations
```{r}
corrplot(NFLCorr, method="color")
corrplot(NFLCorr, method="number")
```


## We can see that in ranked order the most important factors are:
## 1.average_yards_for at **.83**
## 2.turnover_differential at **.70**
## 3.qb_ranking at **-.62**
## 4.third_down_cr at **.61**
## 5.def_rank at **-.58**
## 6.division_strength at **-.42**
## 7.qb_scr at **.25** *but above qb_cap because qb_scr has a higher corr with average_**yards_for*
## 8.qb_cap at **.25